\normalfont \normalsize \textsc{Exoplanet Patchy Cloud Project} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge Note for last two weeks\\ \horrule{2pt} \\[0.5cm]

### 2015-07-03 summary/reply_to_Daniel_Glenn.tex
replied finally

\title{ 
\normalfont \normalsize 
\textsc{Exoplanet Patchy Cloud Project} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Reply to Daniel \& Glenn\\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

\author{Yifan Zhou}
\date{\normalsize\today} % Today's date or a custom date

\usepackage{scalerel}
\usepackage{calc}
\global\newcounter{embedlevel}
\global\newlength\embedspace
\embedspace=2ex
\setcounter{embedlevel}{1}
\newcommand\embed[1]{%
  \stepcounter{embedlevel}%
  \stretchrel{\rule{0.2ex}{1ex}}{\hspace{1.8ex}\parbox{%
    \textwidth-\value{embedlevel}\embedspace}{%
    \rule{0ex}{2ex}\textbf{\textit{#1}}\rule[-1.3ex]{0ex}{1.3ex}%
  }}%
  \vspace{.5ex}%
  \addtocounter{embedlevel}{-1}%
}
\begin{document}

\maketitle % Print the title
\section{Clarifications}
\embed{
1) How do you scale (if you scale) the residuals you subtract?
}

@@

\embed{
 2) How do the residuals images look like? What is the relative
 fraction of the light that is not subtracted well?
}

\embed{
 3) When you calculate the brightness of the sources, how do you use
 the information of the residuals and the TinyTim-based PSF?
}

These are very important points. However I did not deal with them very
carefully in the fit. As I showed in our previous discussion,
Tinytim does not provide a precise PSF model so that the residual of
tinytim PSF subtraction has a 2\% - 4\% average relative fraction of
original image(mean(residual/image) $\sim$ 2\%-\%4). For the fitting routine I used this
time,  the fluxes of A and B purely calculated from the
amplitudes of the two components of the PSF. I did not count any flux
from the residual model into the fluxes of A or B.

An average relative fraction of 2-4\% of the residual model could be a
significant source of uncertainty. Especially for the case that I
ignored the flux from the residual totally. However, I have not come up
with any ideas on including the residual flux to the final result. I
think we need further discussion about this point.

\embed{ a) When you say you carried out a "two component tinytim PSF
  fit", it is not clear to me what you mean.  I assume the linear
  superposition of two TinyTim PSFs.  But do you mean one for A and
  one for B that are otherwise identical (or perhaps different in some
  manner other than brightness?).  Or do you mean for B (and perhaps
  also A) you have used a combination of TinyTim PSFs that, in
  combination (perhaps with different defocus of color terms?) better
  represent the observed PSF?  }

@@

\embed{
b) To me it is interesting (but not really unexpected) that binning
by "same position angle" (i.e., spacecraft roll angle) improves.
Off-rolling does thermally destablise the PSF to some extent - by
changing the angle to the sub-solar point on the Earth as the
telescope orbits and can drive quasi-breathing modes.  I am a bit
surprised that these stabilize out as well as they seem to do (as
exhibited by the factor of 10 improvement in chisq).  It would be
interesting to know how much of that improvement is do to "same
dither position" and how much to "same roll" (as differently binned).
I am sure they both play together to reduce the residuals, but
knowing this could have influence on how future observations might be
constructed.}

The position dependency of the residual pattern comes from at least
three parts.
\begin{enumerate}
\item  Instrumental as Glenn described 
\item The imperfection of flat
  field is not modeled with TinyTim. 
\item  The PSFs are sampled
  differently at different position with a low sample rate.
\end{enumerate}

@@

\embed{
Overall, these look good; the question is, of course, how much of the
apparent trend is real.  One note here: It is curious how both A and B
have an increase in the first 3 orbits and then a different behavior
in orbits 4-6.}

\embed{
Could you explain how exactly do you determine the normalization
factors for the different angles/dithering positions?}

@@

\section{Discussion and further analysis}
\embed{
Daniel asks: "how much of the apparent trend is real".  This might be
difficult to ascertain.  Clearly the F125W and F160W for A seem well
correlated (1st 3 vs last 3 orbits) , but that correlation possibly
could still be instrumental.  If you took the new light curves as
binned, for B:
}

\embed{
if you average all the points together in each orbit (loosing the
 finer temporal information) is the change in normalized flux for B
 over the six orbits also "consistent" from F125W to F160W **AND** is it
 correlated with A?  It's a little harder to tell (quantitatively) as
 plotted for B simply because it is noisier than A.  In both A and B
 (both bands) the flux (by eye) also seems lower in the last three
 orbits and MAYBE the is a small secular rise in orbits 1-3.  I would
 expect that behavior in A and B to be independent, whereas if
 correalted that may be an instrumental signature.}

I binned the light curve of A and B by orbits using average. According to the result
I obtained, there are no clear correlation/anti-correlation betwee the
fluxes of A and B. Figure \ref{fig:1} presented the orbit-binned light
curves.

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{binned_coor_F125W}
  \includegraphics[width=0.45\textwidth]{binned_coor_F160W}
  \caption{Orbit-binned light curves. Binned curve for B showed a sine
  wave shaped curve}
  \label{fig:1}
\end{figure}

\embed{
This looks quite nice and indeed, the 10.9 hours is not a period that
I would obviously associate with an instrumental artifact.  Have you
tried the same for the F160W LC? It would be a nice verification if
you would get a similar periodicity.}

By eye, unbinned light curve of F160W does not show a sine-wave like
shape. However, in the orbit-binned curve, the light curve of B showed
a sine wave shaped curve as shown in Figure \ref{fig:1}. For F160W LC
of B, The least square fit results in a sine curve with a period of
9.3 hr. I also tried to fit the F160W light curve with a sine curve
that has a fixed period of 10.9 hr. I plotted the two best fit sine
curves together with the original observation points as in Figure
\ref{fig:2}. Considering the large scattering of photometric
measurement of B, it is actually hard to tell from Figure \ref{fig:2} whether
the 9.3 hr light curve fits better than the 10.9 hr light curve.

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.8\textwidth]{sineCurveFit}
  \caption{sinusoidal wave fit to the light curve of 2M1207B. For the
    F160W panel, two curves for periods of 9.3 hr and 10.9 hr are
    plotted.}
  \label{fig:2}
\end{figure}

\embed{
Also, to be consistent, can you please use the same fitting procedure
for A (in both filters) and send similar plots?}

I did the fitting for A in both fittings. The rise in first three
orbits is the main feature that defines the sinusoidal wave. However
if it were truly part of a sin wave, the sine function would not be
well constrained by this small segment. For the light curve of F125W,
the fitting routine found a best fitted curve with a period of 6.86
hr. However the points in the 5th orbit are totally off the fitted
curve. For F160W, the fitting routine failed to converge when fitting
a sine curve to the light curve. Figure \ref{fig:3} presented the
fitted sinusoidal wave and the observational points for 2M1207A with
F125W.

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.8\textwidth]{sineCurveFit_primary}
  \caption{sine wave fitting for 2M1207A.}
  \label{fig:3}
\end{figure}

\embed{
(c) I assume the 10.9 hour fit came from a least-squares analysis --
not quite a full observing/sampling period.  "By eye" it certainly
loooks good, but might be interesting to also do a simple periodogram
analysis, just to see if this might be an alias?}

@@

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

>>>>

\title{ 
\normalfont \normalsize 
\textsc{Exoplanet Patchy Cloud Project} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Cross Correlation Test and Preliminary Aperture Photometry Result\\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

\author{Yifan Zhou} % Your name

\date{\normalsize\today} % Today's date or a custom date

\begin{document}

\maketitle % Print the title
Clarifications
>1) How do you scale (if you scale) the residuals you subtract?

@@

> 2) How do the residuals images look like? What is the relative fraction of the light that is not subtracted well?     
> 3) When you calculate the brightness of the sources, how do you use
> the information of the residuals and the TinyTim-based PSF?

These are very important points. However I did not deal with them very
carefully in my previous fit. As I showed in our previous discussion,
Tinytim does not provide a precise PSF model so that the residual of
tinytim PSF subtraction has a 2% - 4% average relative fraction of
original image(mean(residual/image) ~ 2%-%4). For the fitting routine I used this
time,  the fluxes of A and B purely calculated from the
amplitudes of the two components of the PSF. I did not count any flux
from the residual model into the fluxes of A or B.

An average relative fraction of 2-4% of the residual model could be a
significant source of uncertainty. Especially for the case that I
ignored the flux from the residual at all. However, I have not come up
with any ideas on including the residual flux to the final result. I
think we need further discussion about this point.

>a) When you say you carried out a "two component tinytim PSF fit", it is not clear to me what you mean.  I assume the linear superposition of two TinyTim PSFs.  But do you mean one for A and one for B that are otherwise identical (or perhaps different in some manner other than brightness?).  Or do you mean for B (and perhaps also A) you have used a combination  of TinyTim PSFs that, in combination (perhaps with different defocus of color terms?) better represent the observed PSF?

@@

>b) To me it is interesting (but not really unexpected) that binning
>by "same position angle" (i.e., spacecraft roll angle) improves.
>Off-rolling does thermally destablise the PSF to some extent - by
>changing the angle to the sub-solar point on the Earth as the
>telescope orbits and can drive quasi-breathing modes.  I am a bit
>surprised that these stabilize out as well as they seem to do (as
>exhibited by the factor of 10 improvement in chisq).  It would be
>interesting to know how much of that improvement is do to "same
>dither position" and how much to "same roll" (as differently binned).
>I am sure they both play together to reduce the residuals, but
>knowing this could have influence on how future observations might be
>constructed.

The position depandency of the residual pattern comes from at least
three parts.

1. Instrumental as Glenn described
2. The imperfection of flat field is not modeled with TinyTim.
3. The PSFs are sampled differently at different position with a low
sample rate.

@@

> Overall, these look good; the question is, of course, how much of the
> apparent trend is real.  One note here: It is curious how both A and B
> have an increase in the first 3 orbits and then a different behavior
> in orbits 4-6.

>Could you explain how exactly do you determine the normalization
>factors for the different angles/dithering positions?

@@

# Discussion and further analysis

> Daniel asks: "how much of the apparent trend is real".  This might be
> difficult to ascertain.  Clearly the F125W and F160W for A seem well
> correlated (1st 3 vs last 3 orbits) , but that correlation possibly
> could still be instrumental.  If you took the new light curves as
> binned, for B:

> if you average all the points together in each orbit (loosing the
>  finer temporal information) is the change in normalized flux for B
>  over the six orbits also "consistent" from F125W to F160W **AND** is it
>  correlated with A?  It's a little harder to tell (quantitatively) as
>  plotted for B simply because it is noisier than A.  In both A and B
>  (both bands) the flux (by eye) also seems lower in the last three
>  orbits and MAYBE the is a small secular rise in orbits 1-3.  I would
>  expect that behavior in A and B to be independent, whereas if
>  correalted that may be an instrumental signature.

I binned the light curve of A and B by orbits. According to the result
I obtained, there are no clear correlation/anti-correlation betwee the
fluxes of A and B.

![Orbit-binned light curve, F125W](./binned_coor_F125W.pdf
"orbit-binned light curve, F125W")
![Orbit-binned light curve, F160W](./binned_coor_F160W.pdf
 "orbit-binned light curve, F160W")

> This looks quite nice and indeed, the 10.9 hours is not a period that
> I would obviously associate with an instrumental artifact.  Have you
> tried the same for the F160W LC? It would be a nice verification if
> you would get a similar periodicity.

By eye, light curve of F160W does not show a sine-wave like
shape. Thus I do not trust the result of a least square fit very
much. The least square fit results in a sine curve with a period of
9.26 hr. I also tried to fit the F160W light curve with a sine curve
that has a fixed period of 10.9 hr. I plotted the two best fit sine
curves together with the original observation.

> Also, to be consistent, can you please use the same fitting procedure
> for A (in both filters) and send similar plots?

I did the fitting for A in both fittings. The rise in first three
orbits is the main feature that defines the sin wave in the
fit. However if it were truly part of a sin wave, the sine function is
not well constrained by this small segment. For the light curve of
F125W, the fitting routine found a best fitted curve with a period of
6.86 hr. However the points in the 5th orbit are totally off the
fitted curve. For F160W, the fitting routine failed to converge when
fitting a sine curve to the light curve.

> (c) I assume the 10.9 hour fit came from a least-squares analysis --
> not quite a full observing/sampling period.  "By eye" it certainly
> loooks good, but might be interesting to also do a simple periodogram
> analysis, just to see if this might be an alias?

@@
